
The default behaviour of the \gls{qmla} software framework is to generate 
a \emph{\gls{results directory}} for every \gls{run} of the algorithm, 
uniquely identified by the date and time the \gls{run} was launched, 
e.g. \ttt{qmla/launch/Jan\_01/12\_34}. 
Most of the figures presented in the main text analyse data from \glspl{run} of the \gls{qmla} framework;
the \gls{results directory} corresponding to each figure are listed (as \emph{Data}) in \cref{table:figure_reproduction},
and all data presented herein can be downloaded from \cite{flynn2021schrodinger}. 
The presented figures are usually available as default analyses through the \gls{qmla} framework, 
and therefore can be reproduced by implementing the corresponding configuration. 
In \cref{table:figure_reproduction} we list the core implementation details 
-- the number of \glspl{experiment} \gls{nexp}, and \glspl{particle}, \gls{nprt} and the \gls{es} -- used to achieve those results.
In some cases, further configuration details are necessary to produce equivalent \glspl{run};
complete details and information are available at \cite{flynn2021schrodinger}.
Instructions for installing, configuring and running the \gls{qmla} software are given in \cref{apdx:software_eg}.

\par  
\section{Structure of results directory}
Within the \gls{results directory}, the outcome of the \gls{run}'s \glspl{instance} are stored, 
with analysis plots broadly grouped as
\begin{easylist}
\ListProperties(Start1=1)
& \ttt{evaluation}: plots of probes and times used as the evaluation dataset. 
& \ttt{instances}: outcomes of an individual \gls{qmla} \gls{instance}, 
    grouped by the \gls{instance} ID. 
    Includes results of training of individual models (in \ttt{model\_training}), 
    as well as sub-directories for anlaysis at the branch level (in \ttt{branches}) and \ttt{comparisons}. 
& \ttt{combined\_datasets}: 
    \ttt{pandas} dataframes containing most of the data used during analysis of the \gls{run}. 
    Note that data on the individual model/instance level may be discarded so some minor analyses can not be 
    performed offline. 
& \ttt{exploration\_strategy\_plots} plots specifically required by the \gls{es} at the \gls{run} level.
& \ttt{champion\_models}: analysis of the models deemed champions by at least one \gls{instance} in the \gls{run}, 
    e.g. average parameter estimation for a model which wins multiple instances. 
& \ttt{performance}: evaluation of the \gls{qmla} \gls{run}, 
    e.g. the  \gls{win rate}  of each model and the number of times each term is found in \glspl{champion model}. 
& \ttt{meta} analysis of the algorithm' implementation, e.g. timing of jobs on each process in a cluster; 
    generally users need not be concerned with these. 
\end{easylist}    
\par


\renewcommand{\arraystretch}{1.25} % space between rows
\setlength{\tabcolsep}{7pt}

\clearpage
\begin{table}[h!]
\thisfloatpagestyle{empty} % caption goes over page number so supressing it
% \begin{sidewaystable}
\begin{center}
    \input{appendix/figures/figure_implementations_top.tex}
\end{center}
\caption[Figure implementation details]{Implementation details for figures used in the main text. 
    For each \emph{Figure}, we list the \emph{Exploration Strategy} used by the \gls{qmla} framework to achieve 
        the corresponding results, which are stored in the \gls{results directory} labelled by \emph{Data}.
        We list the number of \glspl{experiment}, \gls{nexp}, and \glspl{particle}, \gls{nprt}, used in the training of all models
        within that \gls{run}. 
        Equivalent \glspl{run} of \gls{qmla} can be launched as outlined in \cref{apdx:software_eg}.
    Continued in \cref{table:figure_reproduction_contd}.
}
\label{table:figure_reproduction}
% \end{sidewaystable}
\end{table}

\clearpage
\begin{table}[h!]
    \begin{center}
        \input{appendix/figures/figure_implementations_bottom.tex}
    \end{center}
    \caption[Figure implementation details continued]{[Continued from \cref{table:figure_reproduction}] 
        Implementation details for figures used in the main text.
        For each \emph{Figure}, we list the \emph{Exploration Strategy} used by the \gls{qmla} framework to achieve 
        the corresponding results, which are stored in the \gls{results directory} labelled by \emph{Data}.
        We list the number of \glspl{experiment}, \gls{nexp}, and \glspl{particle}, \gls{nprt}, used in the training of all models
        within that \gls{run}. 
        Equivalent \glspl{run} of \gls{qmla} can be launched as outlined in \cref{apdx:software_eg}.
    }
    \label{table:figure_reproduction_contd}
\end{table}

\clearpage